---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# discrete.time.markov

<!-- badges: start -->
<!-- badges: end -->

Applies the discrete time Markov model (Markov chain) to analyze data (both text and non-text) by computing probabilities of transitions between different states.

Inspired by my Stochastic Models in Management module, as well as my Honors Dissertation, as part of my coursework in the National University of Singapore (NUS) Business School.

## Installation

You can install the released version of discrete.time.markov from my [GitHub](https://github.com/kaiwei-tan/discrete.time.markov) with:

``` r
library(devtools)
install_github("kaiwei-tan/discrete.time.markov")
```

## Examples

This is a basic example, where we generate a random sequence of states and calculate their transition probabilities:
```{r example1}
library(discrete.time.markov)

# Generate random sequence of states
set.seed(57)
states <- sample(c('up', 'down', 'same'), 10000, replace=TRUE)

# Create transition probability matrix
get.transition.matrix(states, option='prob', output_type='matrix')
```

Here is another example involving text. Let each word in our example sentence be considered as a state, and we calculate their transition probabilities accordingly:
```{r example2}
sentence <- 'the quick, brown fox jumps over the lazy dog.'

# Function ignores mid-sentence punctuation i.e. the comma
# Create transition probability matrix
get.transition.matrix.text(sentence, 1, option='prob', output_type='matrix', punct='none')
```

Now let's see what happens when we consider two words in a state and involve the period at the end (ignoring mid-sentence punctuation, each symbol counts as a state regardless of the number of words considered as a state).
```{r example3}
# Create transition probability matrix
get.transition.matrix.text(sentence, 2, option='prob', output_type='matrix', punct='end')
```

We can also use the output of \code{get.transitions.text} (for text data) or \code{get.transitions} (for non-text), which return a dataframe of state transitions and their probabilities, with \code{igraph::graph_from_data_frame} to get a state transition diagram:
```{r example4, warning=FALSE, message=FALSE, fig.width=8, fig.height=8}
library(magrittr)
library(igraph)

lyrics <- c('never gonna give you up', 'never gonna let you down')

# Create dataframe of state transitions and probabilities
lyrics_transitions <- get.transitions.text(lyrics, 1, option='prob', punct='none')

# Plot graph
igraph::graph_from_data_frame(lyrics_transitions) %>%
  plot(edge.label=lyrics_transitions$prob, vertex.color='white')
```
